Modelling BCG vaccination in the UK

### 2019-05-03 index/01-introduction.Rmd
updated wordcount
main conversion for sutherland complete
bump packrat :(

@@

The BCG vaccine was developed in 1921 and was introduced to the UK in 1953. Globally, it has been shown to offer variable protection that may reduce over time.[@TheWorldHealthOrganization:2018va] However, there is strong evidence that BCG offers high levels of protection for children, and more generally within the UK born population.[@Roy2014] It remains the only TB vaccine with over 100 million doses given globally each year. Serious side effects are very rare but scarring commonly occurs at the site of injection. In 2005, the UK withdrew the universal BCG program for those at school age and introduced a targeted program of vaccination for babies that were deemed to be at high risk.[@Zwerling2011a] This was motivated by several years of declining transmission, the evidence of high levels of protection in children and a belief that other control measures would be more cost-effective.[@Zwerling2011a] Since this change in policy, declining incidence appears to support this decision.[@PHE2017] However, due to TB’s complex dynamics, the long-term effects are difficult to predict.

@@

>>>>

```{r}
## Wordcount: 2811
```

@@

The BCG vaccine was developed in 1921 and was introduced to the UK in 1953. Globally, it has been shown to offer variable protection that may reduce over time.[@TheWorldHealthOrganization:2018va] However, there is strong evidence that BCG offers high levels of protection for children, and more generally within the UK born population.[@Roy2014] It remains the only licensed TB vaccine with over 100 million doses given globally each year. Serious side effects are very rare but scarring commonly occurs at the site of injection. In 2005, the UK withdrew the universal BCG program for those at school age and introduced a targeted program of vaccination for babies that were deemed to be at high risk.[@Zwerling2011a] This was motivated by several years of declining transmission, the evidence of high levels of protection in children and a belief that other control measures would be more cost-effective.[@Zwerling2011a] Since this change in policy, declining incidence appears to support this decision.[@PHE2017] However, due to TB’s complex dynamics, the long-term effects are difficult to predict.

@@

* Abbott S, Christensen H, Brooks-Pollock E. *Reassessing the evidence for universal school-age Bacillus Calmette Guerin (BCG) vaccination in England and Wales*, doi: https://doi.org/10.1101/567511

### 2019-05-03 index/index.Rmd
bump packrat :(

---
author: 'Samuel Abbott'
date: 'April 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "36, 969"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---

>>>>

---
author: 'Samuel Abbott'
date: 'April 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "41,218"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---
